---
title: "WallStreetBets"
output: html_document
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../") })
---

Esben Kran

## Presentation

An explorative data visualization of different aspects of the [WallStreetBets subforum on Reddit](https://reddit.com/r/wallstreetbets) and its interaction with the stock market value of an array of stocks.

```{r Read data, echo=FALSE, message=FALSE, warning=FALSE}
pacman::p_load(plotly, tidyverse)
ticker_df <- read_csv("../data/ticker_df.csv")
```

## The market close value of the stock

The value of the selected stock on market close by day.

```{r close, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=8}
ticker_df %>% 
  filter(date > "2021-01-01") %>%
  group_by(ticker) %>%
  mutate(ticker=as.factor(ticker)) %>% 
  plot_ly(x=~date, y=~close, type="scatter", mode="lines", color=~ticker, visible="legendonly")

```

## Proportion of forum posts containing the symbol

The proportion of forum posts that contain the symbol in either uppercase or lowercase.

```{r prop, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=8}
ticker_df %>% 
  filter(date > "2021-01-01") %>%
  group_by(ticker) %>%
  mutate(ticker=as.factor(ticker)) %>% 
  plot_ly(x=~date, y=~prop, type="scatter", mode="lines", color=~ticker, visible="legendonly")

```

## The sentiment of all posts regarding this symbol

The sentiment calculated by VADER for the selected stock per day.

```{r sentiment, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=8}
ticker_df %>% 
  filter(date > "2021-01-01") %>%
  group_by(ticker) %>%
  mutate(ticker=as.factor(ticker)) %>% 
  plot_ly(x=~date, y=~sentiment, type="scatter", mode="lines", color=~ticker, visible="legendonly")

```